\chapter{Discussion} \label{discussion}
The result was somewhat surprising, the greedy algorithm that I thought would be the best algorithm in this simulation was not a huge improvement over the other algorithm. The random algorithm performed better then i expected and the degree algorithm was in some stages better then the greedy algorithm. The independent coverage algorithm performed better or equally good as most of the other algorithm. Toward the end where we choose twenty seed nodes, most of the algorithm performed somewhat the same.

These results can be explained by looking at our simulated social networks. The networks we ran the simulation over was a small graph compared to real world graphs, by choosing at most 20 seed nodes, a large percentage of the graph would be covered. Since the graphs was all connected in a network, the small world effect would result in that every vertex would be subjected to activation. Our global percentage was 0.05. 

One paper showed how implementing a palatalized BFS algorithm on a distributed system reduced the communication times by a factor of 3.5, compared to a common vertex based approach \cite{ParallelBFS2011}.  In scientific application, ,graph based computation is pervasive and often data-intensive, this especially for distributed systems. 

Our simulation runs until there are no more nodes too test. This can explain some of the result we got. Since the simulation runs until no more nodes can be activated, the coverage after 50 runs would most likely activate most of the node. This can result in no distinctive better algorithm. 

For the second simulation, where we stop the simulation after 70\% of the avrage step for greedy algorithm to finish, we got some interesting results. The degree algorithm performed much better then the other algorithms. With the exception of the medium graph, the degree algorithm was clearly better then all of the other algorithms. I suspect that there is some kind of problem I have yet to taken into account. If we ignore the degree algorithms result for a moment, we can see that for the small and medium graph, the greedy algorithm is performing as well as the other algorithms, in the larder graph, the greedy algorithm actually perform worse then the other.

