\chapter{Related works} \label{relatedWork}
We will look at a short overviewe of the current state of the art on different optimization on BFS and seed selections.

\section{Seed selections}
There are many studies that have studied the maximiztion of influence in graph, one particular is by Kempe et al \cite{MaximizeSpread2003}. There different algorithm was proposed to select the most influential seed nodes. 

\subsection{Parallelization of BFS}
parallelization of the breadth first search is known to give poor performance on chache based systems due to the irregular memory accesses of graph data structure \cite{xia2009topologically}.




There are many studies studied the Maximization of influence in graph \cite{MaximizeSpread2003}.  Kempe et al proposed the greedy algorithm that this report have used. There are different studies that have looked at this problem, among those are \cite{InfluenceMax}, where the scalability of the greedy algorithm was discussed. From \cite{InfluenceMax} and our experiments, the greedy algorithm does not scale well with larger graphs. Domingos and Richardson studied how information diffusion can serve as viral marketing \cite{ViralMarketing}

Some potentially improvement with hardware design include \cite{HybridBFS2015}, that proposed the hybrid FPGA-CPU architecture. Where a FPGA-CPU hybrid BFS architecture was designed. They also showed how to view BFS as matrix-vector multiplication on Boolean semirings. 

As we can see, there are many different research around this subjects, even tho there aren't many that looks at how to accelerate seed selection and the Independent cascade model in hardware.

The optimization to graph traversal is a heavily researched field. There are multiple different studies that have proposed different hardware solution for optimizing BFS \cite{ScalableGraphEx}-\cite{DirectOptimizeBFS}. Different strategies of parallise BFS have been proposed here \cite{ParallelBFS2011}. 

\cite{ScalableGraphEx} proposed a BFS for advanced multi-core processor that are scalable , enhances memory locality and cache utilization with an innovative data layout.

One optimization aspect, the high level synthesis have been getting some attention lately. \cite{HLSready2015} shows that HLS might be a viable optimization for FPGA design. 

