\chapter{Introduction} \label{intro}

\begin{list_type}  
\item Most real world graphs are sparse graph
\item Many real world applications can be converted to graph traversal
\item Many solution, Parralizatino, different structure, algorithms, harware implementation, etc \ldots 
\item Some of the current solution
\item why is it important to improve this type of problems
\item How can this benefit from improvement
\item how are we solving the problem
\item Why we choose our solution(hardware acceleration not really explored)
\item how the result was.
\item why use HLS(because an interesting solution, able to test multiple solution in a short implementation time.)
\item 
\end{list_type}

Most real world graph can be coverted over to sparse matrix. examples are social network sites such as facebook and Twitter, other networks such as fans following bloggers or celebertie, and social network where each person is connected to each other via friendships or work. By looking at how data propagate through the network, we can from there find important informations, examples would be how disease spreads through a åpopulation, how a viral video or meme can spread through the internett, the studies can even be used during viral marketing. $Data diffusion$ is the effect where data is propagated through sucha a network, from one node, spreading to another node via edges connecting between them. We can see how data diffusion is applicable in different social field, much like how we mentionened earlied with spreading disease through a population, censorships of the internett in China, viral marketing and social experiments like the small world experiments. One key aspect of the Data diffusioon, is the selection of seed nodes, the nodes that are activated in the initiation time. Those nodes will start the spread of information thorugh the network and in theory infect the entire network, main reason for choosing the essential nodes as seed nodes can be seen as vaccination during flue season. If there are a finite amount of vaccines available, who should be vaccinated to prevent the outbreak? Thus choosing the best candidates would be the most important task. Another examples would be to market a new product by giving away free samples or the product. The reciver will then potentially influence its peer and thus boosting sale. Such studies of such sparse network is important and usefull. There are different algorithms to traverse sucjh graph, one commonly known algorithm for traversing such a agraph is known as $Breadth first search$. The breadth first search traverse the network systematihichally, itteration through each lever of the network. 

For information diffusion or data diffusion, there are two main cases that we can look at, independent cascade model and threshold model. independent cascade model can be looked at as during flue season, each carrier of the flue have a cance to pass the flue to another person. An activation of infection based on a percentage is known as the ICM, independent cascade model. The Linear thershold model, can be looked at as a new product being promoted, each node or person will adopt the new product if a certain number of its friends have bought it, a certain threshold is reached. This is known as the Linear thereshold model, where the activation is desided by the amount of activated neighbours to that node. 

The seed selection algorithm is a NP hard problem, to select the seeds, we would have to run the algorithm for every node and their equivalent combination, for n nodes that would mean $n^2$ itterations. There are different optimization schemes that would reduce computation time, one that we would explore in this paper is optimization through hardware design. 

One field that lately have been getting some attention is the High Level Synthesis(HLS).  HLS takes high level code and synthesis it to machine codes and creaeting a optimal IP-core. The advantage with HLS is that unlike traditional hardware design, HLS converst high level languages such as C and C++ over to VHDL. This alows a much more flexible and productive implementation of the ip-core, you can test different solutions of the implementation by changing the C/C++ code and resynthesis to test different solution. The user would also not need to know how to write in traditional machine language. 

By having a dedicated machine designed to solve the seed selection problem, we can utilize it to have a quick way to simulate disease and viral marketing. graph traversal is also an important subject and applicable in many field. Simulation how disease spread, finding critical poerson to vaccinate, important link to censore to censore content. 

There are multiple benefits of designing a hardware solution to solve such a problem, such a algorithm have require multiple runs to solve such a task.


HLS have matured much since the previous year, the idea of HLS have been worked on in the last year. Some of the pros with the HLS is that hardware design/FPGA design and implementation can be risen above the low level and give software programer the chance to implement specific designe and testing differend scheme and optimization would be easier to test with High Level Synthesis.